Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-15 paper/v2/paper-edited.tex
0,1,2

\author{%
Ryan Beckett\\
  \affaddr{Princeton University}\\
  \email{rbeckett@princeton.edu}
\and
Ratul Mahajan\\
  \affaddr{Microsoft Research}\\
  \email{ratul@microsoft.com}
\and
Todd Millstein\\
  \affaddr{University of California, Los Angeles}\\
  \email{todd@cs.ucla.edu}
\and
Jitu Padhye\\
  \affaddr{Microsoft Research}\\
  \email{padhye@microsoft.com}
\and
David Walker\\
  \affaddr{Princeton University}\\
  \email{dpw@princeton.edu}
}

@@

\textbf{Abstract---}
We develop a system called \sysname to help network operators with a challenging and error prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex distributed protocols.
%
\sysname allows operators to specify their objectives naturally, describing high-level constraints and preferences on the types of paths that traffic should take through their network or other networks.
%using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
%
Our compiler automatically translates these specifications to a collection of BGP router configurations.
% that can execute on existing commodity hardware.
%
We introduce data structures and algorithms that guarantee that the compiled, distributed configurations correctly implement the routing policy under all possible combinations of failures.
%
We use \sysname to specify and compile the configurations of real
data center and backbone networks.  We show that, despite its strong guarantees, it scales to topologies with hundreds to thousands of routers.

@@

It is well known that configuring networks is error
prone and such errors can lead to disruptive network
downtimes~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
For instance, a recent misconfiguration led to an hour-long, nation-wide outage for Time Warner's backbone network~\cite{time-warner}; and a major BGP-related incident makes international news every few months~\cite{bgpmon}.

@@

A fundamental reason for the prevalence of misconfigurations is the
semantic mismatch between the intended high-level
policies and the low-level configurations.
Many policies involve network-wide properties---prefer a certain neighbor,
never announce a particular destination externally,
use a particular path only if another fails---but configurations describe the behavior of
individual devices.
%
Operators therefore must manually decompose network-wide policy into
device behaviors, such that policy-compliant behavior results from the distributed interactions of
these devices.
%
Policy-compliance must be ensured not only under normal
circumstances but also during failures.  The need to reason
about possible failures exacerbates the challenge
for network operators.  As a result, configurations that work
correctly in failure-free environments have nonetheless been found to violate key
network-wide properties when failures occur~\cite{batfish}.

To reduce configuration errors, many practitioners have a adopted a template-based
approach~\cite{hatch,thwack}, in which common tasks are captured as parameterized templates.
%
%More powerful still are systems like
%ConfigAssure~\cite{narain:lisa05,narain+:configassure}, which use SAT solving
%and model finding tools to fill in parameters in configurations while
%ensuring key correctness constraints are satisfied.
%One step further, systems like
%ConfigAssure~\cite{narain:lisa05,narain+:configassure} use SAT solving
%and model finding tools to correctly and consistently fill in some parameters.
%
While templates help ensure certain kinds of consistency across devices,
they do not provide fundamentally different abstractions from existing configuration languages
or bridge the semantic divide between network-wide policies and device-level configuration.
%They do not provide fundamentally different abstractions
%from existing configuration languages and
Thus, they still require operators to
manually decompose policies into device behaviors.

Configuration analysis tools~\cite{batfish,feamster+:rcc} have been developed as a complementary approach for reducing misconfigurations by checking that the low-level configurations match high-level operator intent. However, such tools cannot help operators come up with the configuration in the first place. Further, today's tools can only check correctness under concrete failure scenarios, rather than under all possible failures.

@@

The BGP configurations produced by our compiler are
guaranteed to be policy-compliant in the face of
{\em arbitrary} failures.\footnote{In this paper we assume that BGP is the only control plane protocol running in the network or the other protocols are correctly configured and do not have adverse interactions with BGP~\cite{igp-correctness1,igp-correctness2}.} This does not mean that the implementation is always
able to send traffic to its ultimate destination
(\EG in the case of a network partition), but rather that it always respects the
centralized policy, which may include dropping traffic when there is no route.
%
In this way, we provide network operators
with a strong guarantee that is otherwise impossible to achieve
today.
However, some policies simply cannot be implemented correctly in BGP in
 the presence of arbitrary failures.  We develop new
algorithms to detect such policies
and report our findings to the operators, so they may fix the policy
specification at compile time rather than experience undesirable
behavior after the configurations are deployed.
%We also analyze route aggregation to detect the possibility of failure-induced black-holes.

@@

In implementing their policy, each network operator assumes that
neighboring ASes correctly implement BGP and honor contracts related
to MEDs and communities. \sysname makes the same assumption when
deriving BGP configurations for a network.

The combination of arbitrary import and export filters and route selection policies at individual routers make BGP a highly flexible routing protocol. That flexibility, however, comes at the cost of it being difficult to configure correctly.

>>>>

\author{%
Ryan Beckett\\
  \affaddr{Princeton University}
  %\\
  %\email{rbeckett@princeton.edu}
\and
Ratul Mahajan\\
  \affaddr{Microsoft Research}
  %\\
  %\email{ratul@microsoft.com}
\and
Todd Millstein\\
  \affaddr{University of California, Los Angeles}
  %\\
  %\email{todd@cs.ucla.edu}
\and
Jitu Padhye\\
  \affaddr{Microsoft Research}
  %\\
  %\email{padhye@microsoft.com}
\and
David Walker\\
  \affaddr{Princeton University}
  %\\
  %\email{dpw@princeton.edu}
}

@@

%\textbf{Abstract---}
%We develop a system called \sysname to help network operators with a challenging and error prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex distributed protocols.
%%
%\sysname allows operators to specify their objectives naturally, describing high-level constraints and preferences on the types of paths that traffic should take through their network or other networks.
%%using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
%%
%Our compiler automatically translates these specifications to a collection of BGP router configurations.
%% that can execute on existing commodity hardware.
%%
%We introduce data structures and algorithms that guarantee that the compiled, distributed configurations correctly implement the routing policy under all possible combinations of failures.
%%
%We use \sysname to specify and compile the configurations of real
%data center and backbone networks.  We show that, despite its strong guarantees, it scales to topologies with hundreds to thousands of routers.

\textbf{Abstract---}
We develop \sysname, a language and a compiler to help network operators with a challenging, error-prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex, distributed protocols.
%
The language allows operators to specify their objectives naturally, using high-level constraints and ordered preferences on paths that traffic should take.
%through their network or other networks.
%using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
%
The compiler automatically translates these specifications to router-level BGP configurations, using a novel data structure that compactly encodes the flow of routing information along policy-compliant paths.
%It uses We introduce data structures and algorithms that
It guarantees that the compiled configurations correctly implement the specified policy under all possible combinations of failures.
%
We use \sysname for data center and backbone networks of a large cloud provider. We find that our language can effectively express their policies and, despite its strong guarantees, our compiler scales to topologies with hundreds or thousands of routers.

@@

It is well known that configuring networks is error
prone and such errors can lead to disruptive 
downtimes~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
For instance, a recent misconfiguration led to an hour-long, nation-wide outage for Time Warner's backbone network~\cite{time-warner}; and a major BGP-related incident makes international news every few months~\cite{bgpmon}.

@@

A fundamental reason for the prevalence of misconfigurations is the
semantic mismatch between the intended high-level
policies and the low-level configurations.
Many policies involve network-wide properties---prefer a certain neighbor,
never announce a particular destination externally,
use a particular path only if another fails---but configurations describe the behavior of
individual devices.
%
Operators must manually decompose network-wide policy into
device behaviors, such that policy-compliant behavior results from the distributed interactions of
these devices.
%
Policy-compliance must be ensured not only under normal
circumstances but also during failures.  The need to reason
about all possible failures exacerbates the challenge
for network operators.  As a result, configurations that work
correctly in failure-free environments have nonetheless been found to violate key
network-wide properties when failures occur~\cite{batfish}.

To reduce configuration errors, operators are increasingly adopting an 
approach in which common tasks are captured as parameterized templates~\cite{hatch,thwack}.
%
%More powerful still are systems like
%ConfigAssure~\cite{narain:lisa05,narain+:configassure}, which use SAT solving
%and model finding tools to fill in parameters in configurations while
%ensuring key correctness constraints are satisfied.
%One step further, systems like
%ConfigAssure~\cite{narain:lisa05,narain+:configassure} use SAT solving
%and model finding tools to correctly and consistently fill in some parameters.
%
While templates help ensure certain kinds of consistency across devices,
they do not provide fundamentally different abstractions from existing configuration languages
or bridge the semantic divide between network-wide policies and device-level configuration.
%They do not provide fundamentally different abstractions
%from existing configuration languages and
Thus, they still require operators to
manually decompose policies into device behaviors.

As a complementary approach, configuration analysis tools can help reduce misconfigurations by checking if low-level configurations match high-level policy~\cite{batfish,feamster+:rcc}. However, such tools too cannot help operators with the challenging task of generating configurations in the first place.

%Further, today's tools cannot verify correctness under concrete failure scenarios, rather than under all possible failures.

@@

The BGP configurations produced by our compiler are
guaranteed to be policy-compliant in the face of
{\em arbitrary} failures.\footnote{We assume that BGP is the only routing protocol running in the network or the other protocols are correctly configured and do not have adverse interactions with BGP~\cite{igp-correctness1,igp-correctness2}.} This guarantee does not mean that the implementation is always
able to send traffic to its ultimate destination
(\EG, in the case of a network partition), but rather that it always respects the
centralized policy, which may include dropping traffic when there is no route.
%
In this way, we provide network operators
with a strong guarantee that is otherwise impossible to achieve
today.
However, some policies simply cannot be implemented correctly in BGP in
 the presence of arbitrary failures.  We develop new
algorithms to detect such policies
and report our findings to the operators, so they may fix the policy
specification at compile time rather than experience undesirable
behavior after the configurations are deployed.
%We also analyze route aggregation to detect the possibility of failure-induced black-holes.

@@

The combination of arbitrary import and export filters and route selection policies at individual routers make BGP a highly flexible routing protocol. That flexibility, however, comes at the cost of it being difficult to configure correctly.
When configuring BGP, network operators assume that
neighboring ASes correctly implement BGP and honor contracts for MEDs and communities. \sysname makes the same assumption when
deriving BGP configurations for a network.
